\section{Notable Course Projects}
\cventry{Spring 2023}{}{\href{https://github.com/Parsa2820/BeeGFS-Benchmark}{Advanced Operating Systems \faGithub}}{Prof. Asadi}{}{
Contributing to a team of two, I was involved in deploying, benchmarking, and tuning a BeeGFS file system cluster.
}
\cventry{Spring 2023}{}{\href{https://github.com/Parsa2820/es-project}{Embedded Systems \faGithub}}{Prof. Ansari}{}{
Contributing to a team of four in designing and implementing a smart water container system, integrating hardware components like Raspberry Pi, proximity sensor, and water level sensors, coupled with a Django-based web app.
}
\cventry{Spring 2022}{}{\href{https://github.com/Parsa2820/os-project}{Operating Systems \faGithub}}{Prof. Kharrazi}{}{
This project was based on Berkeley's CS162 course curriculum.
}
\cventry{Spring 2022}{}{\href{https://github.com/Parsa2820/cn-project}{Computer Networks \faGithub}}{Prof. Jafari}{}{
Developed a command-line-based video streaming service in a three-member team.
}
\cventry{Spring 2021}{}{\href{https://github.com/Parsa2820/dsd-projects}{Digital Systems Design \faGithub}}{Prof. Ejlali}{}{
Completed a series of diverse projects in the field of digital system design, including subleq processor, TCAM design, Verilog code generation, dataflow to behavioral model conversion, and various other hardware design challenges.
}
\cventry{Fall 2022}{}{\href{https://github.com/sad-project}{Systems Analysis and Design \faGithub}}{Prof. Mostafazadeh}{}{
Collaborated within a six-member team to design and implement a file-sharing service. Leveraged technologies such as Django, Docker, and Minio while adhering to Agile methodology for efficient development and delivery.
}
\cventry{Fall 2021}{}{\href{https://github.com/Parsa2820/cd-project}{Compiler Design \faGithub}}{Prof. Boreshban}{}{
Collaborated in the creation of a C subset language implemented in Python.
}
\cventry{Spring 2021}{}{\href{https://github.com/Parsa2820/pl-project}{Design of Programming Languages \faGithub}}{Prof. Izadi}{}{
Collaborated in the creation of a Python subset language implemented in Racket.
}