\section{Research Experience}
\cventry{Sep 2024--Present}{Graduate Research Assistant}{Network Research Laboratory}{University of Toronto}{Supervisor: Prof. Jorg Liebeherr}{
	\begin{itemize}
		\item Working on a large-scale environmental sensing platform using LoRa mesh network.
		      % \item Building on top of the works done in the lab (synchronous network), we want to design asynchronous network.
		\item Contributing to IoT projects including large-scale deployments.
		      % \item LoRa empowers us to customize every little parts of the networking stack above physical layer!
	\end{itemize}
}
\cventry{Feb 2023--Dec 2023}{B.Sc. Thesis}{Distributed and Multi-agent Systems Laboratory}{Sharif University of Technology}{Supervisor: Prof. Mohammad Izadi}{
	\begin{itemize}
		\item Contributed to a distributed computing simulation platform built upon the Cloudsim.
		      % \item Gained valuable insights into cloud, fog, and edge computing environments.
	\end{itemize}
}

\cventry{May 2023--Feb 2024}{Research Assistant}{Cyber-Physical Systems Laboratory}{Sharif University of Technology}{Supervisor: Prof. Mohsen Ansari}{
	\begin{itemize}
		\item Conducted research applying metaheuristic algorithms to the fog computing task scheduling.
		      % \item Worked with the CloudSim simulator and assessed the metrics of the scheduling algorithms.
	\end{itemize}
}

\cventry{Jan 2022--May 2022}{Research Assistant}{Algorithm Laboratory}{Sharif University of Technology}{Supervisor: Dr. Arash Vaezi}{
	\begin{itemize}
		\item Studied the realm of distributed systems, especially blockchain technology.
		      % \item Co-authored a comprehensive survey paper on attacks within distributed systems.
	\end{itemize}
}